Paper Figures

### 2019-08-27 PaperFigures.Rmd
added in proliferation data

```{r load data}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
CD4<-read.csv("ICS_CD4_clean.csv")
CYT<-read.csv("ICS_CD4_Cytokine_clean.csv")
PHEN<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
OG<-read.csv("OG_CD4_bulk_summary_clean.csv")
OGPHEN<-read.csv("OG_CD4_OG_summary_clean_NAs.csv")
OG.IFNg<-read.csv("OG_CD4_OG.IFNg_summary_clean_NAs.csv")
OG.GT<-read.csv("OG_CD4_OG.GT_summary_clean_NAs.csv")
luminex<-read.csv("/Applications/Old Computer/Day Lab/Luminex/Clean Data/Luminex_combined_background.txt")
```

#All groups
Dont worry I can change this so the ns bars don't show up, especially for the cytokines since I have no idea why that giant NS is there. But for now I'm leaving them so we know.
```{r}
cd4<-plot_filter(subset(CD4, CD4$Stim=="UN"))
cyt<-plot_filter(subset(CYT, CYT$Stim=="PMA"))
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))
og<-plot_filter(subset(OG, OG$Stim=="SEB"))
ogphen<-plot_filter(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))

allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, scales="free", ncol=4)+
    labs(y="(%) Total CD4+ T cells")+
    theme(legend.position="bottom")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))

allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, scales="free", labeller = cyt_groups, ncol=4)+
    labs(y="(%) Total CD4+ T cells")+
    theme(legend.position="bottom") 
```

#Healthy Adults
*Is this superfluous now?*  
####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.width=15, fig.height=8}
melt<-melt(subset(CYT, CYT$Stim=="PMA"), 
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
th_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))

@@

####LTBI individuals coinfected with S. mansoni have higher Mtb peptide-specific cytokine production, specifically due to higher production of IFNγ
```{r, narrow down ltbi data}
cyt<-filter_ltbi(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))
og<-filter_ltbi(subset(OG, OG$Stim=="PEP"))
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
oggt<-filter_ltbi(subset(OG.GT, OG.GT$Stim=="PEP"))
```

@@

#TB 
```{r, narrow down tb data}
cyt<-filter_tb(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_tb(subset(PHEN, PHEN$Stim=="PEP"))
```
####Similar to QFT+, individuals with active TB, co-infected with S. mansoni maintain function Mtb-specific CD4+ T cell cytokine production. There are higher frequencies of TH1/2 cytokine co-producing CD4+ T cells amongst SM+ individuals, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still TH1 cytokine producing cells.
*Again this is where I need an aesthetics opinion*

@@

```{r, fig.width=15, fig.height=8}
#graph phenotype
melt<-melt(phen, id.vars=c("TB", "SM"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

@@

*I maybe want to do some analysis about the fact that now higher frequencies of cells express T-bet and/or GATA3 and that there seems to be a preferential expansion of CCR4+ cells but I honestly don't know how to test that*

```{r og main four markers, fig.width=16, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))
melt$variable<-factor(melt$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

@@

```{r og phenotype, fig.width=16, fig.height=8}
#graph phenotype
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._._.", names(ogphen)))
test<-filter(melt, variable!="x_x_x_x")
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")
```

####Furthermore, IFNγ and TNFa are also the two dominant cytokines produced when analyzed by luminex. The concentration of all cytokines measured by luminex are equivalent between SM- and SM+ groups.
```{r luminex, fig.width=12, fig.height=16}
lum<-filter_ltbi(subset(luminex, luminex$Stim=="PEP"))
names(lum)<-gsub("IL", "IL-", names(lum))
names(lum)<-gsub("IFNg", "IFNγ", names(lum))
names(lum)<-gsub("TNFa", "TNFα", names(lum))

melt<-melt(lum, id.vars=c("TB", "SM"), measure.vars=grep("pg", names(lum)))
melt$variable<-gsub("_pg.ml", "", melt$variable)
melt$variable<- factor(melt$variable, levels=c("TNFα", "IFNγ", "IL-21", "IL-17A", "IL-22", "IL-10", "IL-4", "IL-5", "IL-13"))
booleanplot(melt, "SM", "value", ltbi.cols)+facet_wrap(~variable, scales="free")+labs(y="pg/mL")
```

@@

#Supplementary

```{r ics phenotyping, fig.width=16, fig.height=8}
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))

@@

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

@@

>>>>

```{r load data}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
CD4<-read.csv("ICS_CD4_clean.csv")
CYT<-read.csv("ICS_CD4_Cytokine_clean.csv")
PHEN<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
OG<-read.csv("OG_CD4_bulk_summary_clean.csv")
OGPHEN<-read.csv("OG_CD4_OG_summary_clean_NAs.csv")
OG.IFNg<-read.csv("OG_CD4_OG.IFNg_summary_clean_NAs.csv")
OG.GT<-read.csv("OG_CD4_OG.GT_summary_clean_NAs.csv")
OG.th1<-read.csv("OG_CD4_OG.TH1_summary_clean_NAs.csv")
luminex<-read.csv("/Applications/Old Computer/Day Lab/Luminex/Clean Data/Luminex_combined_background.txt")
```

#All groups
Statistics were performed using the Mann-Whitney U test for non-parametric data. P-values <0.05 were considered significant.
```{r}
cd4<-plot_filter(subset(CD4, CD4$Stim=="UN"))
cyt<-plot_filter(subset(CYT, CYT$Stim=="PMA"))
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))
og<-plot_filter(subset(OG, OG$Stim=="SEB"))
ogphen<-plot_filter(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

tf<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, ncol=2)+
    theme(legend.position="none") +
    labs(y="(%) Total CD4+ T cells")

melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("CXCR3", "CCR4"))

sm<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, ncol=2)+
    theme(legend.position="none")

cowplot::plot_grid(tf, sm)

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))

one<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, scales="free", labeller = cyt_groups, ncol=2)+
    labs(y="(%) Total CD4+ T cells")+
    theme(legend.position="none")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4"))

four<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, scales="free", labeller = cyt_groups, ncol=1)+
    theme(legend.position="none")+
    coord_cartesian(ylim=c(0,7))

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL13"))

thirteen<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, scales="free", labeller = cyt_groups, ncol=1)+
    theme(legend.position="none")+
    coord_cartesian(ylim=c(0,3))

cowplot::plot_grid(one, four, thirteen, ncol=3, rel_widths=c(7.5,3.75, 3.75))
```

```{r pvals for ifng and tnfa}
y<-split(cyt,cyt$SM) 
A<-lapply(y, function(g) kruskal.test(IFNg~TB, g))
B<-lapply(y, function(g) kruskal.test(TNFa~TB, g))

pval<-c(A$`SM-`$p.value, A$`SM+`$p.value, B$`SM-`$p.value, B$`SM+`$p.value)
comparison<-c("SM- IFNγ", "SM+ IFNγ", "SM- TNFα", "SM+ TNFα")
kable(cbind(comparison, pval))
```

####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.width=15, fig.height=8}
melt<-melt(subset(CYT, CYT$Stim=="PMA"), 
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
th_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))

@@

####LTBI individuals coinfected with S. mansoni have higher Mtb peptide-specific cytokine production, specifically due to higher production of IFNγ
```{r, narrow down ltbi data}
cyt<-filter_ltbi(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))
```

@@

#TB 
```{r, narrow down tb data}
cyt<-filter_tb(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_tb(subset(PHEN, PHEN$Stim=="PEP"))
```

####Similar to QFT+, individuals with active TB, co-infected with S. mansoni maintain function Mtb-specific CD4+ T cell cytokine production. There are higher frequencies of TH1/2 cytokine co-producing CD4+ T cells amongst SM+ individuals, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still TH1 cytokine producing cells.
*Again this is where I need an aesthetics opinion*

@@

```{r receptor on gata3, fig.width=7.5, fig.height=8}
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("TH1_GATA3CCR4", "TH1_GATA3CXCR3"))
melt$variable<-gsub("TH1_", "", melt$variable)
melt$variable<-gsub("GATA3", "GATA3+", melt$variable)
melt$variable<-gsub("CXCR3", "CXCR3+", melt$variable)
melt$variable<-gsub("CCR4", "CCR4+", melt$variable)

baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*15))+
    coord_cartesian(ylim=c(0,15))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")
```

#Proliferation Assay
##All Groups Responses to SEB
```{r}
og<-plot_filter(subset(OG, OG$Stim=="SEB"))
ogphen<-plot_filter(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

```{r, proliferation and total cyt, fig.width=15, fig.height=8}
melt<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars=c("OG_freq", "IFNg_freq", "TNFa_freq", "IL4_freq"))

groups <- as_labeller(c("IFNg_freq" = "IFNγ", 
                    "TNFa_freq" = "TNFα", "IL4_freq" = "IL-4", "OG_freq" = "Proliferation"))

allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups, ncol=4)+
    labs(y="(%) Total CD4+ T cells")+
    theme(legend.position="bottom") 
```

```{r, cyt from proliferating, fig.width=12, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg_freq", "TNFa_freq", "IL4_freq"))

groups <- as_labeller(c("IFNg_freq" = "IFNγ", 
                    "TNFa_freq" = "TNFα", "IL4_freq" = "IL-4"))

allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups, ncol=3)+
    labs(y="(%) Proliferating CD4+ T cells")+
    theme(legend.position="bottom") 
```

```{r, marker on proliferating, fig.width=15, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet_freq", "GATA3_freq", "CXCR3_freq", "CCR4_freq"))

melt$variable<-gsub("_freq", "", melt$variable)
melt$variable<-factor(melt$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", ncol=4)+
    labs(y="(%) Total CD4+ T cells")+
    theme(legend.position="bottom") 
```

##Mtb-Specific Responses in LTBI
```{r}
og<-filter_ltbi(subset(OG, OG$Stim=="PEP"))
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
oggt<-filter_ltbi(subset(OG.GT, OG.GT$Stim=="PEP"))
ogth1<-filter_ltbi(subset(OG.th1, OG.GT$Stim=="PEP"))
```

@@

*I maybe want to do some analysis about the fact that now higher frequencies of cells express T-bet and/or GATA3 and that there seems to be a preferential expansion of CCR4+ cells but I honestly don't know how to test that*
###On proliferating cells
```{r og main four markers, fig.width=16, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))
melt$variable<-factor(melt$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")

@@

###On TH1 proliferating cells
```{r og th1 main four markers, fig.width=16, fig.height=8}
melt<-melt(ogth1, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))
melt$variable<-factor(melt$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")

#Luminex Data

####Furthermore, IFNγ and TNFa are also the two dominant cytokines produced when analyzed by luminex. The concentration of all cytokines measured by luminex are equivalent between SM- and SM+ groups.

*Honestly I will have to just remake the whole thing a couple times and stitch them together to fix the axes so just ignore them for now*
```{r luminex, fig.width=12, fig.height=16}
lum<-filter_ltbi(subset(luminex, luminex$Stim=="PEP"))
names(lum)<-gsub("IL", "IL-", names(lum))
names(lum)<-gsub("IFNg", "IFNγ", names(lum))
names(lum)<-gsub("TNFa", "TNFα", names(lum))

melt<-melt(lum, id.vars=c("TB", "SM"), measure.vars=grep("pg", names(lum)))
melt$variable<-gsub("_pg.ml", "", melt$variable)
melt$variable<- factor(melt$variable, levels=c("TNFα", "IFNγ", "IL-21", "IL-17A", "IL-22", "IL-10", "IL-4", "IL-5", "IL-13"))

booleanplot(melt, "SM", "value", ltbi.cols)+facet_wrap(~variable, scales="free")+
    labs(y="pg/mL")
```

@@

#Supplementary
###Peptide-Specific Cytokine Production  
```{r, fig.width=15, fig.height=8}
melt<-melt(subset(CYT, CYT$Stim=="PEP"), 
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
th_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))

cyt<-filter_hc(melt)
a<-baseplot(cyt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    labs(y="(%) CD4+ T cells")+coord_cartesian(ylim=c(0,.2))

cyt<-filter_ltbi(melt)
b<-baseplot(cyt, "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,.2))

cyt<-filter_tb(melt)
c<-baseplot(cyt, "SM", "value", tb.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,.2))

##Some Boolean Cytokine graphs will go here for posterity
*but I need to make them pretty and I dont' feel like doing that right now*
```{r}
cyt<-filter_ltbi(CYT[CYT$Stim=="PMA",])
test<-melt(cyt, id.vars=c("TB", "SM"), measure.vars = grep("._._._.|._._.._.", names(cyt)))
test$variable<-factor(test$variable, levels=c(
"G_4_13_T", "G_4_x_T", "G_x_13_T", "G_4_13_x", "x_4_13_T","G_4_x_x", "G_x_13_x","x_4_x_T","x_x_13_T",
"G_x_x_T" , "G_x_x_x","x_x_x_T",
"x_4_13_x","x_4_x_x", "x_x_13_x"
))

G   <-c("+", "+", "+", "+", "-", "+", "+", "-", "-", "+", "+", "-", "-", "-", "-")
il4 <-c("+", "+", "-", "+", "+", "+", "-", "+", "-", "-", "-", "-", "+", "+", "-")
il13<-c("+", "-", "+", "+", "+", "-", "+", "-", "+", "-", "-", "-", "+", "-", "+")
T   <-c("+", "+", "+", "-", "+", "-", "-", "+", "+", "+", "-", "+", "-", "-", "-")

labels <- paste0(G, "\n", T, "\n", il4, "\n", il13)
breaks <- levels(test$variable)

test$th<-"TH1/2"
test$th[grep("._x_x_.", test$variable)]<-"TH1"
test$th[grep("x_._._x|x_._.._x", test$variable)]<-"TH2"
test$th<-factor(test$th, levels=c("TH1/2", "TH1", "TH2"))

booleanplot(test, "variable", "value", ltbi.cols)+facet_grid(~th, scales="free", space="free_x")+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) CD4+ T cells",
         title="PMA")
```

###Peptide Mtb-specific TH1 Cytokine+ Cell Phenotypes
```{r ics phenotyping, fig.width=16, fig.height=8}
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))

@@

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x",ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells",
         title="ICS Assay")

@@

```{r, fig.width=15, fig.height=8}
phen<-filter_tb(subset(PHEN, PHEN$Stim=="PEP"))

#graph phenotype
melt<-melt(phen, id.vars=c("TB", "SM"), measure.vars = grep("TH1_._._._.", names(phen)))
test<-filter(melt, variable!="TH1_x_x_x_x")
test$variable<-gsub("TH1_", "", test$variable)
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

```{r og phenotype, fig.width=16, fig.height=8}
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
#graph phenotype
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._._.", names(ogphen)))
test<-filter(melt, variable!="x_x_x_x")
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Proliferating Mtb-Specific cells")
```
